---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

### Descriptive Statistics

Install package
```{r}
install.packages("ISLR")
```
Get the data
```{r}
library(ISLR)
```

Check the data
```{r}
dataCredit <- Credit
head(dataCredit)
```
Check the dimension of the data
```{r}
dim(dataCredit)
```

See the  values  of one  variable
```{r}
dataCredit$Income
```
Create histogram
```{r}
hist(dataCredit$Income)
```
Sample Mean
```{r}
mean(dataCredit$Income)
```

Sample Median
```{r}
median(dataCredit$Income)
```

Frequency Table
```{r}
table(dataCredit$Ethnicity)
```
```{r}
install.packages("lsr")
```


```{r}
library(lsr)
```


```{r}
modeOf(dataCredit$Education)
```
```{r}
maxFreq(dataCredit$Education)
```
Compute  the  variance  and sd of a variable
```{r}
var(dataCredit$Income)
```
```{r}
sd(dataCredit$Income)
```
Percentile
```{r}
quantile(x = dataCredit$Income , probs = 0.1)
```
```{r}
quantile(x=dataCredit$Income , probs=c(0.25 ,0.50,  0.75))
```
Range
```{r}
range(dataCredit$Income)
```
Interquartile Range
```{r}
IQR(dataCredit$Income)
```
Boxplot
```{r}
boxplot(dataCredit$Income)
```
Correlation

Create a new  data of  income  and  limit
```{r}
newData  <- data.frame(income = dataCredit$Income , limit = dataCredit$Limit)
```

Plotting the data
```{r}
plot(newData$income , newData$limit)
```

Compute the correlation
```{r}
cor(newData)
```

Binomial
```{r}
dbinom(x = 4, size = 10, prob = 1/3)
```
```{r}
pbinom(q = 4, size = 10, prob = 1/3)
```
```{r}
qbinom(p = 0.75,  size = 10, prob = 1/3)
```

```{r}
rbinom(n = 50, size = 10, prob = 1/3)
```

Normal
```{r}
dnorm(x = 1, mean = 1, sd = 0.1)
```

Cumulative  probability P(< 0.7), given a standard  normal
```{r}
pnorm(q = 0.7, mean = 0, sd = 1)
```
Percentile  25 of a standard  normal
```{r}
qnorm(p = 0.25,  mean = 0, sd = 1)
```
Sampling  from a normal  distribution  with  mean
```{r}
dataNorm  <- rnorm(n = 100, mean = 160, sd = 2)
```
Plot  the  corresponding  histogram
```{r}
hist(dataNorm)
```
