---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

### Discrete Random Variable

For example, we are tossing a 1000 IDR coin n = 10 times and let X be the number of angklungs after all tosses. Knowing that the probability of angklung appears in one toss is p=1/3,
what is the probability that we get X = 4 angklungs out of n = 10 tosses?

```{r}
dbinom(x = 4, size = 10, prob = 1/3)
```

X<=4
```{r}
pbinom(q=4, size = 10, prob = 1/3)
```

Percentile ke-75
```{r}
qbinom(p = 0.75, size = 10, prob = 1/3)
```

Simulasi 50 binomial random variabel
```{r}
rbinom(n = 50, size = 10, prob = 1/3)
```

## Continuous Random Variable
Mencari nilai density = 1 pada distribusi normal dengan rata2 = 1 dan standard deviasi = 0.1
```{r}
dnorm(x = 1, mean = 1, sd = 0.1)
```

Mencari CMF dengan X < 0.7 pada standard normal
```{r}
pnorm(q = 0.7, mean = 0, sd = 1)
```

Persentil ke-25 pada standard normal
```{r}
qnorm(p = 0.25, mean = 0, sd = 1)
```

Sampling 100 data, dengan rata2 = 160 dan SD = 2
```{r}
dataNorm <- rnorm(n = 100, mean = 160, sd = 2)
dataNorm
```

Plot histogram
```{r}
hist(dataNorm)
```














