---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
### The required package
To perform linear equations in R, we need to install a package called **matlib**.
To install the package, write the command below:

```{r}
#install.packages("matlib")
```

Load the package
```{r}
library(matlib)
```


### Equations in two unknowns
Suppose we have a linear system,

$$
\begin{alignat*}{7}
5x &&\; - \;&& 4y             &&\; = \;&& -10  \\
-x &&\; + \;&& y             &&\; = \;&& 2 
\end{alignat*}
$$
that can be represented in a matrix form 

$$
\begin{bmatrix}
	5 & -4 \\
  -1 & 1
  \end{bmatrix}
    \begin{bmatrix}
	  x_{1} \\
    x_{2}
	\end{bmatrix}
	=
	\begin{bmatrix}
	-10 \\
	2 
	\end{bmatrix}
$$
that is, $$Ax=b$$, and we have $$ x = A^{-1}b$$

#### Create and show the equation
```{r}
A <- matrix(c(5, -4, -1, 1), 2, 2, TRUE)
b <- c(-10, 2)
showEqn(A, b)
```
#### Find solution
```{r}
Solve(A,b)
```                   


#### Plot the equation
Use plotEqn() for equations with two-variable equations and use plotEqn3d for three-variable equations.
```{r}
plotEqn(A,b)
```   


#### Reduced echelon form
```{r}
echelon(A,b)
```

```{r}
echelon(A, b, verbose=TRUE, fractions=TRUE)
```

```{r}
echelon(A,b, verbose=TRUE)
```


